\section{Math Extension}
The basic extensions for Math.

\mb{Math.mod(i, n): number}
Returns a positive number $x$, where $i = k * n + x, (x > 0)$.
\mb{Math.range(start = 0, end, step = 1): [ ]}
Generates an array of range from \cd{start} (inclusive) to \cd{end} (exclusive), with that \cd{step}.
\mb{Math.randomInteger(a = 0, b): number}
Gets a random integer $x$, where $ a \leq x \leq b $.
 
\subsection{Statistics}
The basic statistics extension that is located in \cd{Math.Stats.*}

\mmb{max(arr): number}
Gets the max number of an array.
\mmb{min(arr): number}
Gets the min number of an array.
\mmb{sum(arr): number}
Gets the sum of an array.
\mmb{mean(arr): number}
Gets the average of an array.
\mmb{var(arr): number}
Gets sample variance of an array.
\mmb{stddev(arr): number}
Gets the standard deviation of an array.
\mmb{linearLeastSquare(X,  Y, fn=(x=\textgreater x) ): [number, number]}
Gets the \cd{[a, b]}, where $fn(Y) = a \cdot fn(X) + b$. passes \cd{Math.log} to get linear least square for $Y = c \cdot X^a$.


\subsection{Math.Point}
The point for the vector.

\mmb{new Math.Point(arr)}
Builds new point by coordinates array.

\subsection{Math.Vector}
The vector in $n$ dimension.

\mmb{new Math.Vector(arr)}
Builds new vector by coordinates array.
\mmb{new Math.Vector(arr1, arr2)}
Builds new vector by coordinates array of two point.
\mmb{new Math.Vector(point1, point2)}
Builds new vector by two Math.Point.

\mmb{Math.Vector.norm(vec): number}
Gets the length of the vec.
\mmb{Math.Vector.dot(v1, v2): number}
Calculates the \cd{dot} result of two vectors.
\mmb{Math.Vector.cos(v1, v2): number}
Calculates the \cd{cos} result of two vectors.

\mmb{norm(): number}
Gets the length of the vec itself.
\mmb{dot(that): number}
Calculates the \cd{dot} result of this and that.
\mmb{cos(that): number}
Calculates the \cd{cos} result of this and that.